% !Mode:: "Tex:UTF-8"
\begin{resume}

  \section*{发表的学术论文} % 发表的和录用的合在一起

  \begin{enumerate}[{[}1{]}]
  \addtolength{\itemsep}{-.36\baselineskip}% 缩小条目之间的间距，下面类似
  \item Qin Y, Shen S, Wu Q, et al. Complementary Synthesis for Encoder with Flow
Control Mechanism [J]. accepted by ACM Transactions on Design Automation of
Electronic Systems.（SCI检索，WOS：xxx，IDS：xxx）

  \item Qin Y, Shen S, Wu Q, et al.Complementary Synthesis for Pipelined Encoder.
accepted by Asia Pacific Design Automation Conference,2016.（EI检索，WOS：xxx，IDS：xxx）

  \item Qin Y, Shen S, Wu Q, et al.Complementary Synthesis for Encoders with
Pipeline and Flow Control Mechanism.
accepted by Haifa Verification Conference,2015.（EI检索，WOS：XXX，IDS：XXX）

  \item Ying Qin, ShengYu Shen, Jingzhu Kong, Huadong Dai:
Cloud-Oriented SAT Solver Based on Obfuscating CNF Formula. APWeb Workshophs 2014: 188-199（EI检索）

  \item Ying Qin, ShengYu Shen, Yan Jia:
Structure-aware CNF obfuscation for privacy-preserving SAT solving. MEMOCODE 2014: 84-93（EI检索）

  \item Shen S, Qin Y, Wang K, et al. Synthesizing Complementary Circuits Automatically
[J/OL]. IEEE Transactions on Computer-Aided Design of Integrated Circuits
and Systems. 2010, 29 (8): 29:1191–29:1202. （SCI检索，WOS：xxx，IDS：xxx）

  \item Shen S, Qin Y, Xiao L, et al. A Halting Algorithm to Determine the Existence of
the Decoder [J/OL]. IEEE Transactions on Computer-Aided Design of Integrated
Circuits and Systems. 2011, 30 (10): 30:1556–30:1563.（SCI检索，WOS：xxx，IDS：xxx）

  \item Shen S, Qin Y, Wang K, et al. Inferring Assertion for Complementary Synthesis
[J/OL]. IEEE Transactions on Computer-Aided Design of Integrated Circuits
and Systems. 2012, 31 (8): 31:1288–31:1292.（SCI检索，WOS：xxx，IDS：xxx）


  \item Shen S, Qin Y, Zhang J. Inferring assertion for complementary synthesis [C/OL]. In
Proceedings of the 2011 International Conference on Computer-Aided Design. San
Jose, CA, USA, 2011: 404–411. （EI检索，WOS：XXX，IDS：XXX）


  \end{enumerate}

  \section*{申请专利} % 有就写，没有就删除
  \begin{enumerate}[{[}1{]}]
  \addtolength{\itemsep}{-.36\baselineskip}%
  \item 董德尊, 鲁晓佩, 廖湘科, 赖明澈, 陆平静, 王绍刚, 徐炜遐, 肖立权, 庞征斌等. 基于多维尺度变换的虫洞拓扑识别方法 (专利号：201310057009)
  \item 李姗姗, 廖湘科, 刘晓东, 吴庆波, 戴华东, 彭绍亮, 王蕾, 付松龄, 鲁晓佩, 郑思. 一种基于图形处理单元的影响最大化并行加速方法(专利号：201210248732.3)
  \end{enumerate}

  \section*{参与主要科研项目} % 有就写，没有就删除
  \begin{enumerate}[{[}1{]}]
  \addtolength{\itemsep}{-.36\baselineskip}%
  \item 国家自然科学基金“面向通讯应用的自动对偶综合方法研究”（项目编号：61070132）
  \end{enumerate}
\end{resume}
